\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.48in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\definecolor{accent}{HTML}{3F6212}
\titleformat{\section}{\large\bfseries\color{accent}}{}{0pt}{}[\vspace{-3pt}\rule{\linewidth}{0.4pt}]
\titlespacing*{\section}{0pt}{5pt}{3pt}
\setlist[itemize]{leftmargin=13pt,itemsep=0.5pt,topsep=1.5pt,parsep=0pt}
\newcommand{\role}[3]{\textbf{#1} \hfill \textit{#2}\\[-1pt]\textit{#3}}

\begin{document}
{\Huge\bfseries Fred Zirbel}\\[2pt]
{\large Principal Security Analyst \textbar{} Detection Engineering \textbar{} Incident Response}\\[3pt]
\href{mailto:me@fredzirbel.com}{me@fredzirbel.com} \quad
\href{https://fredzirbel.com}{fredzirbel.com} \quad
\href{https://www.linkedin.com/in/fredzirbel}{linkedin.com/in/fredzirbel} \quad
\href{https://github.com/fredzirbel}{github.com/fredzirbel}

\section*{Summary}
Principal Security Analyst leading high-velocity investigations across identity, email, endpoint, and cloud telemetry. Sustains a 16-minute average time to investigation across 300+ monthly investigations; engineered 500+ suppression filters to reduce recurring noise. Builds open-source investigation and detection tooling in Python.

\section*{Experience}
\role{Principal Security Analyst}{Jul 2026 - Present}{Critical Start, Plano, TX}
\begin{itemize}
  \item Own phishing, malware, and identity investigations and coordinated remediation in MDR operations supporting 2,500+ customer environments and 30+ integrated security products.
  \item Sustain a 16-minute average TTI across 300+ monthly investigations; guide customer response decisions and mentor analysts on evidence quality, scope, and escalation readiness.
\end{itemize}
\role{Senior Security Analyst}{Jul 2025 - Jul 2026}{Critical Start, Plano, TX}
\begin{itemize}
  \item Correlated email, identity, network, and endpoint telemetry with custom KQL to reconstruct attacker actions and scope cross-tenant campaigns.
  \item Engineered and quality-reviewed 500+ KVP and regex suppression filters, eliminating thousands of recurring false positives.
\end{itemize}
\role{Security Analyst}{Oct 2024 - Jul 2025}{Critical Start, Plano, TX}
\begin{itemize}
  \item Triaged identity, phishing, malware, and endpoint alerts across Defender, Sentinel, CrowdStrike, and SentinelOne; produced client-ready escalations and remediation guidance.
\end{itemize}

\section*{Selected Projects}
\textbf{SOC Box} \textbar{} Python, FastAPI, Playwright, Docker, KQL \hfill \href{https://github.com/fredzirbel/SOCBox}{GitHub}\\[-1pt]
Self-hosted analyst workspace for eight-dimension URL detonation, streamed results, IP enrichment, bulk analysis, and Defender XDR/Sentinel hunting-query generation. Includes OIDC/service-token auth, SSRF protection, rate limiting, and automated security checks.\\[2pt]
\textbf{SIGIL} \textbar{} Python, Sigma, Splunk, Sentinel, MITRE ATT\&CK \hfill \href{https://github.com/fredzirbel/SIGIL}{GitHub}\\[-1pt]
Detection-as-code pipeline that validates Sigma schemas, converts to SPL/KQL, tests rules against sample logs, and maps coverage gaps across the Enterprise ATT\&CK matrix.

\section*{Skills}
\textbf{Investigation:} Microsoft Defender XDR, Sentinel, CrowdStrike Falcon, Cortex XDR, SentinelOne, Splunk ES, Sumo Logic\\
\textbf{Detection and engineering:} KQL, Sigma, MITRE ATT\&CK, Python, FastAPI, Docker, GitHub Actions, OpenSearch

\section*{Education and Certifications}
\textbf{M.S., Cybersecurity and Information Assurance}, Western Governors University \quad
\textbf{B.S., Information Systems}, The University of Texas at Arlington\\
CompTIA SecurityX (CASP+), CySA+, PenTest+, Security+; ISC2 Certified in Cybersecurity \quad \textbf{CISM - In Progress}
\end{document}
